Mplus Results

### 2017-08-23 mplus-results-manuscript.Rmd
update to cfa tables

# Read in information from the .out files
# read in lgmm data info 
output = readModels()
names(output[[1]])
names(output[[1]]$parameters) # get names of different param output.

# get fit summaries from output files
df.sums = lapply(output, function(x) x$summaries)
df.sums[[1]] # check

@@

# get parameters from output files -- for metric models 
# -------------------------------------------------------
# TO DO: need to get standardized estimates
df.params = lapply(output, function(x) data.frame(x$parameters$unstandardized$METRIC.MODEL))
nrow(df.params[[2]])

@@

@@

@@

sums.dt = data.table(combine.sums)
wide.fit <- data.table::dcast(sums.dt[sums.dt$Model=="METRIC MODEL", with=T],
                  groups ~ Model , 
                  value.var = fits)

@@

#dim(wide.fit)
wide.fit2 = wide.fit
colnames(wide.fit2) = c(rep(c(""),7))

kable(wide.fit2, 
      booktabs=T,
      format="html",
      caption='Goodness of fit') %>%
    kable_styling(bootstrap_options = c("striped")) %>%
  add_header_above(c("Groups"=1,
                     "Chi-Square"=1,
                     "DF"=1,
                     "LL"=1,
                     "CFI"=1,
                     "aBIC"=1,
                     "RMSEA"=1)) #%>%
  # group_rows("Weight", 1, 7) %>%
  # group_rows("Height", 8, 14) %>%
  # group_rows("WFL", 15, 21)

@@

>>>>

# Read in information from the .out files
# read in lgmm data info 
output = readModels()
names(output[[1]])
names(output[[1]]$parameters) # get names of different param output.
```

```{r}
# get fit summaries from output files
df.sums = lapply(output, function(x) x$summaries)
df.sums[[1]] # check

@@

# get parameters from output files -- for metric models 
# -------------------------------------------------------
# TO DO: need to get standardized estimates
df.params = lapply(output, function(x) data.frame(x$parameters$unstandardized$METRIC.MODEL))
nrow(df.params[[2]])
df.params[[1]]

@@

# Need to figure out a way to add the groups for each of there unique combos of 
# paramHeader and param.
# order of groups: age (3), re (5), sex (2) and year (5)

# note that the f1.by values are duplicated are the same for factor loadings
# because they are held constant across groups.
# for age: 1 = 12-13 2 = 14-16 3 = 17-19
# for race/ethnicity:  1 = MA 2 = OH 3 = NHW 4 = NHB 5 = OTH
# for sex of child: 1 = male 0 = female
# for year: 2003 = y2003 2005 = y2005 2007 = y2007 2009 = y2009 2011 = y2011

names(output)

names(combine.params)
table(combine.params$unstandardized.Group)
nrow(combine.params)
head(combine.params)

length(unique(paste0(combine.params$unstandardized.paramHeader, 
                     combine.params$unstandardized.param)))

combine.params$group = rep(paste0(names(output)),
                              sapply(output, function(x) 
                                nrow(data.frame(x$parameters$unstandardized$METRIC.MODEL))))

@@

nrow(combine.params[combine.params$groups=="Age",])

@@

sums.dt = data.table(combine.sums)
wide.fit <- data.table::dcast(sums.dt,
                  groups + Model ~ . , 
                  value.var = fits)

@@

#dim(wide.fit)
wide.fit2 = wide.fit
wide.fit2$Model = factor(wide.fit2$Model, 
                         labels=c("Configural",
                                  "Metric",
                                  "Scalar"))
kable(wide.fit2[,-1], 
      booktabs=T,
      format="html",
      caption='Goodness of fit',
      col.names=c("Model", "ChiSq", "df", "LL", "CFI", "aBIC", "RMSEA")) %>%
    kable_styling(bootstrap_options = c("striped")) %>%
  group_rows("Age", 1, 3) %>%
  group_rows("Gender", 4, 6) %>%
  group_rows("Race/ethnicity", 7, 9) %>%
  group_rows("Time", 10, 12)

@@

# make a table of parameters
names(combine.params)
head(combine.params$groups)

sums.dt = data.table(combine.sums)
wide.params <- data.table::dcast(setDT(combine.params),
                  groups +  unstandardized.Group + unstandardized.paramHeader + unstandardized.param  ~ .,
                  value.var = c("unstandardized.est"))

# note that the f1.by values are duplicated are the same for factor loadings
# because they are held constant across groups.
# for age: 1 = 12-13 2 = 14-16 3 = 17-19
# for race/ethnicity:  1 = MA 2 = OH 3 = NHW 4 = NHB 5 = OTH
# for sex of child: 1 = male 0=female
# for year: 003 = y2003 2005 = y2005 2007 = y2007 2009 = y2009 2011 = y2011

wide.params

num.rows.p = table(wide.params$groups)
num.rows.p
num.rows.p.c = cumsum(num.rows.p)

sub.wide.p = wide.params[wide.params$unstandardized.paramHeader=="Intercepts", ]
num.rows.p.c = cumsum(table(sub.wide.p$groups))

kable(wide.params[wide.params$unstandardized.paramHeader=="Intercepts", -1], 
      booktabs=T,
      format="html",
      caption='Goodness of fit') %>%
    kable_styling(bootstrap_options = c("striped")) %>%
  group_rows("Age", 1, num.rows.p[1]) %>%
  group_rows("Gender", num.rows.p.c[1]+1, num.rows.p.c[2]) %>%
  group_rows("Race/Ethnicity", num.rows.p.c[2]+1, num.rows.p.c[3]) %>%
  group_rows("Time", num.rows.p.c[3]+1, num.rows.p.c[4])
